Information Closure Theory of Consciousness

### 2019-09-01 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

		%% stochasticity at microscopic levels
		Despite the evolutionary advantage of forming NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging. NTIC requires the predictability of the system state and is therefore impeded by noise in the system. Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise source es throughout, including sensory, cellular, electrical, and synaptic noises. For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.

@@

        %% Our argument
		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining microscopic neural states. Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state. In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}. Neural systems, therefore, can form more stable and deterministic state transitions and be more capable to form NTIC processes at certain coarse-grained macroscopic levels.

		Coarse-graining is considered as a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.

		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust. This is a common neural coding scheme that we see in a large number of neurophysiological studies. For example, individual neural spikes in a transient time span are stochastic, but they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}. Neurons encode stimulus intensity by increasing or decreasing firing rate. \citep{kandel2000principles}.  \citep{stein2005neuronal}. In contrast, rate codes are relatively stable and are highly robust against noise caused by the variation of inter-spike intervals. The robustness is direct consequence of the many to one map used.

>>>>

		%% stochasticity at microscopic levels
		Despite the evolutionary advantage of having NTIC processes in a system, however, to create NTIC with a highly stochastic process is challenging. NTIC requires the predictability of the system state and is therefore impeded by noise in the system. Information processing at the microscopic levels (the cellular levels) in neural systems suffer from multiple environmental noise sources throughout, including sensory, cellular, electrical, and synaptic noises. For example, neurons have large trial-to-trial variability at the cellular level, and are subject to thermal fluctuations and other physical noises \citep{faisal2008noise}.

@@

        %% Our argument
		However, we argue that, neural systems can form NTIC at certain macroscopic levels through coarse-graining microscopic neural states. Coarse-graining refers to many-to-one functions which aggregate microscopic states to a macroscopic state. In other words, a number of different micro-states realise the same value of the macro-variable \citep{price2007causation}. Neural systems, therefore, can form more stable and deterministic state transitions and be more capable of forming NTIC processes at certain coarse-grained macroscopic levels.

		Indeed, empirical evidence shows that coarse-graining is a common coding strategy in the neural system against ubiquitous stochasticity at microscopic levels.

% 		Although the microscopic levels in the neural system are stochastic and may incapable of forming NTIC processes, the macroscopic processes in the system can still be  stable and robust. This is a common neural coding scheme that we see in a large number of neurophysiological studies.

		For example, albeit the temporal intervals between two consecutive action potentials from individual neurons are stochastic, the firing rate, a temporal coarse-grained variable, represent more meaningful

		they can be coarse-grained as spiking rate variables, known as rate coding \citep{adrian1926impulses, gerstner2002spiking, maass2001pulsed, panzeri2015neural, stein2005neuronal}. Neurons encode stimulus intensity by increasing or decreasing firing rate. \citep{kandel2000principles}.  \citep{stein2005neuronal}. In contrast, rate codes are relatively stable and are highly robust against noise caused by the variation of inter-spike intervals. The robustness is direct consequence of the many to one map used.
